---
title: "Project 2"
author: "Tom Jeon"
date: "September 13, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spanish Translation A/B Test
### Goal

A/B tests play a huge role in website optimization. Analyzing A/B tests data is a very important
data scientist responsibility. More specifically, data scientists have to make sure that results are reliable, trustworthy, and conclusions can be drawn.

Furthermore, companies often run tens, if not hundreds, of A/B tests at the same time. Manually
analyzing all of them would require lot of time and people. Therefore, it is common practice to
look at the typical A/B test analysis steps and try to automate as much as possible. This frees
up time for the data scientists to work on more high level topics.

In this project, you will have to analyze results from an A/B test. Also, you will be asked to
design an algorithm to automate some steps.



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
