---
title: "Project 1"
author: "Tom Jeon"
date: "September 10, 2016"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Conversion Rate
### Goal

Optimizing conversion rate is one of the most common work of a data scientist. The hype of data science has a lot to do with the fact that now we are able to collect all sorts of data about people who buy something on our site as well as people who don't. This gives us a
tremendous opportunity to understand what's working well (and potentially scale it even further)
and what's not working well (and fix it).

The goal of this project is to build a model that predicts conversion rate and, based on the
model, come up with ideas to improve rev􀁝enue.

There are no dates, no tables to join, no feature engineering required, and the problem is pretty straightforward. I think this is a great starting point to get familiar with data science problems.

### The Challenge

We have data about users who use this site: whether they converted or not as well as some of their characteristics such as their country, the marketing channel, their age, whether they are repeat users and the number of pages visited during their session (as a proxy for site activity/time spent on site).

Your task is to:
    - Predict conversion rate.
    - Come up with recommendations for the product team and the marketing team to improve conversion rate.

### Data

The table is "conversion_data". It has information about signed-in users during one session. Each row is a user session.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
